Web data extraction through named entity labeling

### 2018-11-29 tex/article.tex
LSTM explanation.

Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feedforward neural networks, 
RNNs can retain information in their internal state, making them more suitable for processing sequences, 
and consequently for solving text related tasks. In NER, the network outputs one label for each input 
vector as shown in Figure \ref{fig:rnn_network}.

Although RNNs are theoretically capable of learning long term dependencies, in practice 
it becomes difficult due to vanishing gradients. Long short term memory networks (LSTM) were 
introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
they have been popularized since then. LSTM cell implementations vary slightly in the literature.
Our implementation has the following definition:

\begin{flalign*}
\Gamma_i^{<t>} &= \sigma(W_i[x^{<t>},h^{<t-1>}] + b_i) &\\
\Gamma_f^{<t>} &= \sigma(W_f[x^{<t>},h^{<t-1>}] + b_f) &\\ 
c^{<t>}        &= \Gamma_f^{<t>} \circ c^{<t-1>} + \Gamma_i^{<t>} tanh(W_c[x^{<t>},h^{<t-1>}] + b_c) &\\
\Gamma_o^{<t>} &= \sigma(W_o[x^{<t>},h^{<t-1>}] + b_o) &\\
h^{<t>}        &= \Gamma_o^{<t>} \circ tanh(c^{t}) &
\end{flalign*}

@@

where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
forget and output gates, respectively. And $ W $ with a subscript is the weight 
matrix corresponding to that gate. Variable $ c^{<t>} $ is the cell 
state and $ h^{<t>} $ is the hidden state, with the vector $ [x^{<t>},h^{<t-1>}] $ 
being formed by concatenating the current input vector $ x^{<t>} $ and the hidden vector 
from the previous timestep $ h^{<t-1>} $. A visual description of our LSTM cell is 
provided in figure \ref{fig:lstm_cell}.
This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
in that the input gate $ \Gamma_i $ and the forget gate $ \Gamma_f $
do not take input from the previous cell state $ c^{<t-1>} $ and the output gate does
not take input from the current cell state $ c^{<t>} $. The cell state and the control gates 
are what makes the LSTM cell better at modelling long term dependencies in comparison
to a regular RNN.

@@

The neural models were trained with mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
parameters, considering the F1 measure in the validation set. All neural models used 
GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training,
they have a vocabulary size of 400.000 words.
In the case of NER on HTML, word embeddings work similar to a gazetteer. Named entities 
with the same type have similar embeddings, so good word embeddings can achieve exceptional 
performance with little training and without a gazetteer.

>>>>

Recurrent neural networks (RNN) have been succesfully employed on numerous NLP tasks such as
language modelling, POS tagging, speech recognition and NER. Different from feedforward 
neural networks, RNNs can retain information in their internal state, making them more 
suitable for processing sequences, and consequently for solving text related tasks. 
Figure~\ref{fig:rnn_network} describes an RNN for sequence labeling unrolled through multiple 
timesteps. At each timestep, the neural network computes a hidden state $ h_t $ using an input 
vector $ x_t $ and the previous hidden state $ h_{t-1} $, that retains information from past 
iterations. Finally, the RNN produces an output vector $ y_t $ representing the label for that 
timestep. A common definition for an RNN cell is given by the equations:

\begin{flalign*}
h_t &= tanh(W_x x_t + W_h h_{t-1}) &\\
y_t &= softmax(W_y h_t) &
\end{flalign*}

Where $ W_x $, $ W_h $ and $ W_y $ are weight matrices that can be trained with the 
Backpropagation Through Time (BPTT) algorithm. Theoretically, RNNs are capable of learning
and retaining long term dependencies through their internal state $ h_t $. However, in practice,
it becomes difficult due to the vanishing gradient problem. Long short term memory networks (LSTM) were 
introduced by Hochreiter and Schmidhuber \cite{Hochreiter1997} with this problem in mind and 
have been popularized since then.

LSTMs incorporate a memory cell $ c $ in the RNN definition and three gates to control 
the flow of information that comes in and out of the memory cell.
The input gate $ \Gamma_{i} $ controls the amount of new information that will flow into the memory cell,
the forget gate $ \Gamma_{f} $ controls the amount of previous information that will be retained in the memory
cell, and the output gate $ \Gamma_{o} $ controls the amount of information stored in the memory cell that
will be used to compute the output activation of the LSTM unit. LSTM cell implementations vary slightly in 
the literature, so we give the definition for our implementation below:

\begin{flalign*}
\Gamma_{i} &= \sigma(W_i[x_t,h_{t-1}] + b_i) &\\
\Gamma_{f} &= \sigma(W_f[x_t,h_{t-1}] + b_f) &\\ 
\Gamma_{o} &= \sigma(W_o[x_{t},h_{t-1}] + b_o) &\\
c_t      &= \Gamma_{f} \circ c_{t-1} + \Gamma_{i} \circ tanh(W_c[x_{t},h_{t-1}] + b_c) &\\
h_t      &= \Gamma_{o} \circ tanh(c_t) &
\end{flalign*}

@@

where $ \sigma $ is the logistic sigmoid function. $ \Gamma_i $, $ \Gamma_f $, and $ \Gamma_o $ are the input,
forget and output gates, respectively. And $ W $ with a subscript is the weight 
matrix corresponding to that gate. Variable $ c_{t} $ is the cell 
state and $ h_{t} $ is the hidden state, with the vector $ [x_{t},h_{t-1}] $ 
formed by concatenating the current input vector $ x_{t} $ and the hidden vector 
from the previous timestep $ h_{t-1} $. A visual description of our LSTM cell is 
provided in figure \ref{fig:lstm_cell}.

This implementation differs from the LSTM cell described in Huang et al. \cite{Huang2015}
in that the input gate $ \Gamma_i $ and the forget gate $ \Gamma_f $
do not take input from the previous cell state $ c^{<t-1>} $ and the output gate does
not take input from the current cell state $ c^{<t>} $.

The cell state and the control gates 
are what makes the LSTM cell better at modelling long term dependencies in comparison
to a regular RNN.

@@

The neural models were trained with mini batch Stochastic Gradient Descent over 50 epochs with batch size 10,
learning rate 0.01, momentum 0.9 and decay rate 0.05. We used early stopping \cite{Caruana2000} to select the best 
parameters, considering the F1 measure in the validation set. All neural models used 
GloVe 100-dimensional word embeddings \cite{Pennington2014} that were fine tuned during training,
they have a vocabulary size of 400.000 words.
In the case of NER on HTML, word embeddings work similarly to a gazetteer. Named entities 
with the same type have similar embeddings, so good word embeddings can achieve exceptional 
performance with little training and without a gazetteer.
